---
title       : Stopping Distance Prediction
subtitle    : Application Pitch
author      : Mark Knox
job         : Developing Data Products Course Project
framework   : revealjs      # {io2012, html5slides, shower, dzslides, ...}
revealjs    : {theme: solarized, transition: cube}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.height=4, fig.width=6,
                      echo=FALSE, warning=FALSE, message=FALSE)
```

<br><br>
## Stopping Distance Prediction
### Application Pitch
<br><br><br>
Mark Knox   
Developing Data Products Course Project

--- .class #id

## Application Overview
<br>
* Predicts stopping distance based on speed of travel
    + Uses *cars* data set from RStudio
    + Stopping distance is predicted based on linear model
* Application built using shiny library
* Application has 3 tabs:
    + **Main** is where all the work is done
    + **Help** contains overview & usage instructions
    + **Source Code** contains *ui.R* and *server.R* code

--- .class #id 

## Application Need
<br>
* Stopping distance is often underestimated by new drivers
* Stopping distance is dependent on speed of travel
* Many accidents could be prevented if new drivers used this application
    + But not while they are driving
        * because that would be bad...

---

## Application Instructions
<br>

1. Select Speed of Car using slider control on **Main** tab
    + Range: 5 - 200 mph (over 200 mph is just crazy)
2. Click **Predict** button
3. Predicted Stopping Distance (ft) will be shown
    + Including a plot with the predicted data

---

## Application Example
<br>
```{r echo=FALSE}
data(cars)
lm_cars <- lm(dist ~ speed, data=cars)

stopping_distance <- function(speed_in) {
    df_speed <- data.frame(speed = speed_in)
    round(predict(lm_cars, df_speed), 0)
}

input_speed <- 35
pred_dist <- stopping_distance(input_speed)
```
* Selecting **`r input_speed`** mph for Speed of Car
* Will tell you the predicted stopping distance is: **`r paste(pred_dist, "ft")`**
* And display a pretty(?) plot of the predicted data
```{r echo=FALSE}
plot(x=cars$speed, y=cars$dist, col="black",
     main="Stopping Distance",
     xlab="Speed (mph)",
     ylab="Distance (ft)",
     xlim=c(0, max(max(cars$speed), input_speed)),
     ylim=c(0, max(max(cars$dist), pred_dist))
)
abline(lm_cars, col="red", lwd=3)
points(x=input_speed, y=pred_dist, pch=3, col="blue", lwd=4)
lines(x=c(input_speed, input_speed), y=c(0, pred_dist), col="gray60", lty=2)
lines(x=c(0, input_speed), y=c(pred_dist, pred_dist), col="gray60", lty=2)
```
